---
title: "Assignment1"
author: "Jason1823"
date: "Monday, February 16, 2015"
output: html_document
---

**This assignment is accomplished using the file "activity.csv"**

###Here shows the R code for loading and preprocessing the data###

```{r Loading and Preprocessing the data, echo = TRUE }
data <- read.csv("activity.csv")
data$date <- as.Date(data$date, "%Y-%m-%d")
```

###Here is the R code for calculating the total number of steps taken each day###

```{r Total Number of Steps Taken Each Day, echo=TRUE}
datasteps <- data[!is.na(data$steps),]  ##remove the na
tapply(datasteps$steps,datasteps$date,sum)
```

###Here is the R code for calculating the mean of steps taken each day###

```{r Mean of Steps Taken Each Day, echo=TRUE}
tapply(datasteps$steps,datasteps$date,mean)
```

###Here is the R code for calculating the median of steps taken each day###

```{r Median of Steps Taken Each Day, echo=TRUE}
tapply(datasteps$steps,datasteps$date,median)
```

###Here is the code for plotting the average steps taken per 5-minute interval, averaged across all days###

```{r Average Steps per 5-minute Interval, echo=TRUE}
avestepsint <- tapply(datasteps$steps,datasteps$interval,mean)
interval <- names(avestepsint)
plot(interval,avestepsint, type = "l", ylab = "Number of Steps")
```

###Here is the code for calculating the interval with most steps###
```{r Interval that Contains Most Number of Steps, echo = TRUE}
interval[avestepsint == max(avestepsint)]
```

###Imputing missing values

```{r, echo =TRUE}
dataNA <- is.na(data$steps)
sum(dataNA)   ##report the number of missing values

##Strategy of imputing: replace the missing values with the mean of that 5-minute interval
data$interval <- as.character(data$interval)
for(i in seq_along(data$steps)){
    if(is.na(data$steps[i])) 
        data$steps[i] <- avestepsint[data$interval[i]]
}

```

Here is the code for exhibiting the difference of the pattern of steps between weekdays and weekends

```{r, echo=TRUE}
weekdays <- weekdays(datasteps$date)
weekends <- weekdays == "ÐÇÆÚÁù" | weekdays =="ÐÇÆÚÈÕ"
datasteps<- cbind(datasteps,weekends)
week <- character()
for(i in seq_along(datasteps$steps)){
    if(datasteps$weekends[i])  week[i] <- "weekends"
    else
        week[i] <- "weekdays"
    }
datasteps <- cbind(datasteps,week) 
dataweekends <- subset(datasteps,datasteps$week =="weekends") ##split data by weekend or weekdays
dataweekdays <- subset(datasteps,datasteps$week =="weekdays")
weekdayStepsAve <- tapply(dataweekdays$steps,dataweekdays$interval,mean)
weekendStepsAve <- tapply(dataweekends$steps, dataweekends$interval, mean)
par(mfrow = c(2,1))
plot(interval, weekdayStepsAve, ylab ="Number of Steps",type = "l")
plot(interval, weekendStepsAve, ylab ="Number of Steps",type = "l")

```

**Thanks for your investigation**
